HMM Model development

### 2020-10-17 dev/hmm_model_devel.Rmd
Optimize the HMM model by avoiding computation for impossible states

```{r}
adapt_delta <- 0.9

data <- hmm_simulator(5, 10, 2, use_noisy_states = TRUE)

@@

model_single <- stan_model(model_code = single_code)

standata <- make_standata_hmm(data$observed)

if(inherits(model_single, "stanmodel")) {
  fit <- sampling(model_single, data = standata, control = list(adapt_delta = adapt_delta))
} else {
  cmdstan_fit <- model_single$sample(data = standata, adapt_delta = adapt_delta)
  fit <- rstan::read_stan_csv(cmdstan_fit$output_files())
}
evaluation_summary(fit, data$true)

>>>>

```{r}

adapt_delta <- 0.9

data <- hmm_simulator(N_series = 10, N_time = 10, N_mid_states = 2, use_noisy_states = FALSE)
standata <- make_standata_hmm(data$observed)

#Temporary hack
registerS3method("stan_log_lik", class = "rate_hmm", method = stan_log_lik.rate_hmm, envir = asNamespace("brms"))

@@

model_file <- here::here("local_temp_data", "devel_single_model.stan")
write_lines(single_code, path = model_file)
model_single <- cmdstanr::cmdstan_model(model_file)

if(inherits(model_single, "stanmodel")) {
  fit <- sampling(model_single, data = standata, control = list(adapt_delta = adapt_delta))
} else {
  standata$optimize_possible = 0
  cmdstan_fit <- model_single$sample(data = standata, adapt_delta = adapt_delta)
  fit <- rstan::read_stan_csv(cmdstan_fit$output_files())
}
evaluation_summary(fit, data$true)
